### 2019-10-12 ch1_introduction/content.tex
update

IHC (and many other biotechnologies) visualises antigen-antibody reactions by attaching particular molecules to the antibody, such as an enzyme that catalyses a colour-producing reaction, or a fluorescent chemical compound that can re-emit light upon excitation. The use of several colours (wavelengths) allows measuring expression levels of different antibodies simultaneously. Characterising cells in a semi-quantifiable way is labour intensive, however; since it involves acquiring an image of many cells and drawing a contour around each cell (called cell segmentation).
Modern implementations of IHC improve the throughput drastically by using robots and computer software to automate the image acquisition and cell segmentation. Nonetheless, the procedure is still labour intensive as the robots and computer software still needs to be kept in check.

Flow cytometry\cite{fulwyler_electronicseparationbiological_1965} is a technique which circumvents imaging and segmentation issues by having a steady stream of cells run through a laser and measuring the amount of light scattered from those cells. 
Since cells need to be suspended in a buffer, flow cytometry is particularly useful for analysing non-adherent cells such as the many different immune cells in the blood. However, many protocols already exist to extract viable single cells from tissue as well\cite{leelatian_preparingviablesingle_2017}.
Common flow cytometry enables to measure proteins expression levels of millions of cells for 8 different antibodies, though state-of-the-art instrumentation allow detecting up to 27 biomarkers simultaneously\cite{cossarizza_guidelinesuseflow_2017}.

>>>>

IHC (and many other biotechnologies) visualises antigen-antibody reactions by attaching particular molecules to the antibody, such as an enzyme that catalyses a colour-producing reaction, or a fluorescent chemical compound that can re-emit light upon excitation. The use of several colours (wavelengths) allows measuring expression levels of different antibodies simultaneously. Characterising cells in a semi-quantifiable way is labour intensive, however; since it involves acquiring an image of many cells and drawing a contour around each cell (called cell segmentation).
Modern implementations of IHC improve the throughput drastically by using robots and computer software to provide semi-automated image acquisition and cell segmentation\cite{theodosiou_automatedanalysisfish_2007}.

Flow cytometry\cite{fulwyler_electronicseparationbiological_1965} circumvents imaging and segmentation issues by running a steady stream of cells through a laser and measuring the amount of fluorescent light scattered from those cells. 
Since cells need to be suspended in a buffer, flow cytometry is particularly useful for analysing non-adherent cells such as the many different immune cells in the blood. However, many protocols already exist to extract viable single cells from tissue as well\cite{leelatian_preparingviablesingle_2017}.
Common flow cytometry enables to measure proteins expression levels of millions of cells for 8 different antibodies, though state-of-the-art instrumentation allow detecting up to 27 biomarkers simultaneously\cite{cossarizza_guidelinesuseflow_2017}.
